### 2021-11-08 Final Doc/Chapters/Chapter3.tex
Updated Final Docs

\section{Description of the Development of the Artefact}
This section will detail the development of the computer game artefact but will only include specifics on the aspects which were worked on individually - as such the contributions and accompanying processes of the other group members will not be discussed. 
\\\\
Before describing the development life cycle of the artefact, there are some definitions to be aware of:
\begin{enumerate}
\item \underline{User} refers to the real person making use of the artefact.
\item \underline{Player} refers to the in artefact character controlled by a user.
\item A \underline{Level} or \underline{Scene} refers to a specific section within the artefact - for example, the main menu, tutorial and end credits are all scenes while only the tutorial would additionally be classified as a level.
\item A \underline{Prefab} allows for the creation, configuration and storage of a \underline{GameObject} - this being any object within the artefact - with all its components, properties and child GameObjects for easy drag and drop usage.
\item \underline{Character Controller} refers to how the in-game character, the Player, is affected by a user's inputs.
\item The \underline{Raycast} function projects a ray into the scene, returning a boolean value if a target was successfully hit in addition to other information, such as distance.
\item A \underline{Collider} component refers to the shape of an object for the purposes of physical collisions and is invisible.
\item \underline{Layer Mask} refers to an editor based flag that interacts with any raycast or collider based functions to filter out any colliders which are not to be included in generating collisions with.
\item A \underline{Rigid Body} components allows a GameObject to react to the real-time physics engine - this includes gravity, forces, etc.
\item An \underline{Asset} refers to any digital item that you can use in your game or project.
\end{enumerate}

@@

\begin{figure}[H]
\centering
\includegraphics[scale=0.33]{Figures/testold.png}
\caption{Test Scene for Initial Player Movement}
\label{flrtst}
\end{figure}

@@

\begin{figure}[H]
\centering
\includegraphics[scale=0.61]{Figures/floor.png}
\caption{Floor Detection Visualisation (Own Creation)}
\label{floor}
\end{figure}

@@

\begin{figure}[H]
\centering
\includegraphics[scale=1]{Figures/rot.png}
\caption{Object Rotation Set in Editor}
\label{rot}
\end{figure}

@@

\textbf{Ball Return}\\

\textbf{Teleportation and Portal Prefab}\\

\begin{figure}[H]
\centering
\includegraphics[scale=0.33]{Figures/portalconcept.png}
\caption{Original Portal Concept}
\end{figure}

\begin{figure}[H]
\centering
\begin{subfigure}{0.5\textwidth}
  \centering
  \includegraphics[width=1\linewidth]{Figures/finporta.png}
  \caption{Main Portal Asset}
\end{subfigure}%
\begin{subfigure}{0.5\textwidth}
  \centering
  \includegraphics[width=1\linewidth]{Figures/finportb.png}
  \caption{Tutorial Specific Re-colouration}
\end{subfigure}
\caption{Finalised Portal Assest}
\end{figure}

\textbf{Ending a Level}\\

@@

\section{Description of the Development of the Article}
%Comprehensive report on the way in which each phase of the life cycle was applied in the development of this artefact.
This section will detail the development of the article and the specific sprints taken to complete it.

>>>>

\section{Description of the Development of the Artefact}
This section will detail the development of the computer game artefact but will only include specifics on the aspects which were worked on individually - as such the contributions and accompanying processes of the other group members will not be discussed. 
\\\\
Before describing the development life cycle of the artefact, there are some definitions to be aware of:
\begin{enumerate}
\item \underline{User} refers to the real person making use of the artefact.
\item \underline{Player} refers to the in artefact character controlled by a user.
\item A \underline{Level} or \underline{Scene} refers to a specific section within the artefact - for example, the main menu, tutorial and end credits are all scenes while only the tutorial would additionally be classified as a level.
\item A \underline{Prefab} allows for the creation, configuration and storage of a \underline{GameObject} - this being any object within the artefact - with all its components, properties and child GameObjects for easy drag and drop usage.
\item \underline{Character Controller} refers to how the in-game character, the Player, is affected by a user's inputs.
\item The \underline{Raycast} function projects a ray into the scene, returning a boolean value if a target was successfully hit in addition to other information, such as distance.
\item A \underline{Collider} component refers to the shape of an object for the purposes of physical collisions and is invisible.
\item \underline{Layer Mask} refers to an editor based flag that interacts with any raycast or collider based functions to filter out any colliders which are not to be included in generating collisions with.
\item A \underline{Rigid Body} components allows a GameObject to react to the real-time physics engine - this includes gravity, forces, etc.
\item An \underline{Asset} refers to any digital item that you can use in your game or project.
\item A \underline{Tag} is similar to a layer mask.
\end{enumerate}

@@

\begin{figure}[H]
\centering
\includegraphics[scale=0.28]{Figures/testold.png}
\caption{Test Scene for Initial Player Movement}
\label{flrtst}
\end{figure}

@@

\begin{figure}[H]
\centering
\includegraphics[scale=0.665]{Figures/floor.png}
\caption{Floor Detection Visualisation (Own Creation)}
\label{floor}
\end{figure}

@@

\begin{figure}[H]
\centering
\includegraphics[scale=1.25]{Figures/rot.png}
\caption{Object Rotation Set in Editor}
\label{rot}
\end{figure}

@@

\noindent \textbf{Ball Return}\\
The development of this script was initially intended for use during testing only however the group realised that if a user where to throw the ball GameObject to a place that could not reach or access in the game, they would be unable to progress and as such the script was left in the game. 
\\\\
The only functionality this script implements is that when a user makes use of the T key, the ball GameObject will be teleported to their current location. This was accomplished by setting the ball GameObject's position within the scene to slightly above and in front of the player.
\\\\
\textbf{Teleportation and Portal Prefab}\\
In a similar fashion, the teleport script works off the same concept to that of the ball return script. The difference is that the function implemented within this script, \texttt{OnTriggerEnter()}, makes use of the colliders of a GameObject when it overlaps with another GmaeObject and changes the position accordingly.
\\\\
The script can be used in multiple ways as it allows the assignment of both a trigger GameObject and a GameObject to be teleported. When the trigger GameObject collides with the GameObject this script is placed on, the GameObject set to teleport will be teleported. Figure \ref{tp} illustrates examples of how this was done in the Unity Editor.
\begin{figure}[H]
\centering
\begin{subfigure}{0.5\textwidth}
  \centering
  \includegraphics[width=1\linewidth]{Figures/tpp.png}
  \caption{Trigger is the Player}
\end{subfigure}%
\begin{subfigure}{0.5\textwidth}
  \centering
  \includegraphics[width=1\linewidth]{Figures/tps.png}
  \caption{Trigger is the Ball GameObject}
\end{subfigure}
\caption{Examples of when the Player is Teleported}
\label{tp}
\end{figure}

\noindent The main use of this script is i conjunction with the Portal Prefab. This prefab consists of the teleport script, two instances of the moving platform script, two Probuilder GameObjects and a particle system. Figure \ref{portals} shows the two types of Portal Prefabs.

\begin{figure}[H]
\centering
\begin{subfigure}{0.4\textwidth}
  \centering
  \includegraphics[width=1\linewidth]{Figures/finporta.png}
  \caption{Main Portal Asset}
\end{subfigure}%
\begin{subfigure}{0.4\textwidth}
  \centering
  \includegraphics[width=1\linewidth]{Figures/finportb.png}
  \caption{Tutorial Specific Re-colouration}
\end{subfigure}
\caption{Finalised Portal Assest}
\label{portals}
\end{figure}

\noindent \textbf{Moving Platforms}\\
This script works similarly to the rotation script as instead of rotating the object , this script moves an object between two points in a scene. 
\\\\
\textbf{Ending a Level}\\

@@

\newpage
\section{Description of the Development of the Article}
%Comprehensive report on the way in which each phase of the life cycle was applied in the development of this artefact.
This section will detail the development of the article and the specific sprints taken to complete it.
